Approximation as Differentiation

### 2025-04-01 notes.tex
biadditive -> bilinear seems more common.
Rename.

Covered so far:
\begin{itemize}
\item $\CMon$-enriched categories (\secref{cmon-enriched})
\item biproducts (\secref{biproduct})
\item category $\Fam(I,C)$ of $I$-indexed families of objects of $C$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{C}F$ and category of families $\Fam(C)$ (\secref{grothendieck})
\item Examples of useful categories with biproducts:
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FdVect_k$ of finite-dimensional vector spaces over a field $k$ (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\end{itemize}

@@

\input{notes/sec/cmon-enriched}
\input{notes/sec/biproduct}
\input{notes/sec/fam}
\input{notes/sec/set-indexed-product}
\input{notes/sec/grothendieck}
\input{notes/sec/galois}

>>>>

Covered so far:
\begin{itemize}
\item $\CMon$-enriched categories (\secref{cmon-enriched})
\item biproducts and semi-additive categories (\secref{biproduct})
\item category $\Fam(I,C)$ of $I$-indexed families of objects of $C$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{C}F$ and category of families $\Fam(C)$ (\secref{grothendieck})
\item Examples of useful semi-additive categories (\secref{useful-semi-additive-categories}):
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FinVect_F$ of finite-dimensional vector spaces over a field $F$
   (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\end{itemize}

@@

\input{notes/sec/cmon-enriched}
\input{notes/sec/biproduct}
\input{notes/sec/fam}
\input{notes/sec/set-indexed-product}
\input{notes/sec/grothendieck}
\input{notes/sec/useful-semi-additive-categories}

### 2025-04-01 notes/sec/biproduct.tex
biadditive -> bilinear seems more common.
Rename.

Suppose $C$ a $\CMon$-enriched category.

@@

\begin{proposition}
\label{prop:biproduct:from-product-or-coproduct}
Suppose $C$ is $\CMon$-enriched.
\begin{itemize}
\item If $C$ has biproducts given by $(A \biprod B, \biinj_A, \biinj_B, \biproj_A, \biproj_B)$ then $(A
\biprod B, \biproj_A, \biproj_B)$ is a product and $(A \biprod B, \biinj_A, \biinj_B)$ is a coproduct.
\item If $C$ has binary products given by $(A \times B, \proj_1, \proj_2)$ then:
\begin{enumerate}
\item $\prodM{0_{A,B}}{0_{A,C}} = 0_{A,B \times C}$
\item $\prodM{f_1 + g_1}{f_2 + g_2} = \prodM{f_1 + f_2}{g_1 + g_2}$
\item $(A \times B, \biinj_A, \biinj_B, \proj_1, \proj_2)$ is a
biproduct with $\biinj_A: A \to A \times B = \prodM{\id_A}{0_{A,B}}$ and $\biinj_B: B \to A \times B =
\prodM{0_{A,B}}{\id_B}$.
\end{enumerate}
\item If $C$ has binary coproducts given by $(A + B, \inj_1, \inj_2)$ then
\begin{enumerate}
\item $\coprodM{0_{A,C}}{0_{B,C}} = 0_{A + B,C}$
\item $\coprodM{f_1 + g_1}{f_2 + g_2} = \coprodM{f_1 + f_2}{g_1 + g_2}$
\item $(A + B, \inj_1, \inj_2, \biproj_A, \biproj_B)$ is a
biproduct with $\biproj_A: A + B \to A = \coprodM{\id_A}{0_{B,A}}$ and $\biproj_B: A + B \to B =
\coprodM{0_{A,B}}{\id_B}$.
\end{enumerate}
\item If $C$ has a terminal (or initial) object then it is a zero object.
\end{itemize}
\end{proposition}

>>>>

Suppose $C$ a $\CMon$-enriched category. \todo{I think we can also define ``biproduct'' using a universal
property and zero morphisms, which might be nicer as we can then derive rather than assume $\CMon$-enrichment.}

@@

\begin{proposition}
\label{prop:biproduct:from-product-or-coproduct}
Suppose $C$ is $\CMon$-enriched.
\begin{itemize}
\item If $C$ has biproducts $(A \biprod B, \biinj_A, \biinj_B, \biproj_A, \biproj_B)$ then $(A
\biprod B, \biproj_A, \biproj_B)$ is a product and $(A \biprod B, \biinj_A, \biinj_B)$ is a coproduct.
\item If $C$ has binary products $(A \times B, \proj_1, \proj_2)$ then:
\begin{enumerate}
\item $\prodM{0_{A,B}}{0_{A,C}} = 0_{A,B \times C}$
\item $\prodM{f_1 + g_1}{f_2 + g_2} = \prodM{f_1 + f_2}{g_1 + g_2}$
\item $(A \times B, \biinj_A, \biinj_B, \proj_1, \proj_2)$ is a
biproduct with $\biinj_A: A \to A \times B = \prodM{\id_A}{0_{A,B}}$ and $\biinj_B: B \to A \times B =
\prodM{0_{A,B}}{\id_B}$.
\end{enumerate}
\item If $C$ has binary coproducts $(A + B, \inj_1, \inj_2)$ then
\begin{enumerate}
\item $\coprodM{0_{A,C}}{0_{B,C}} = 0_{A + B,C}$
\item $\coprodM{f_1 + g_1}{f_2 + g_2} = \coprodM{f_1 + f_2}{g_1 + g_2}$
\item $(A + B, \inj_1, \inj_2, \biproj_A, \biproj_B)$ is a
biproduct with $\biproj_A: A + B \to A = \coprodM{\id_A}{0_{B,A}}$ and $\biproj_B: A + B \to B =
\coprodM{0_{A,B}}{\id_B}$.
\end{enumerate}
\item If $C$ has a terminal (or initial) object then it is a zero object.
\end{itemize}
\end{proposition}
